---
title: "Good Plot Bad Plot"
author: "Cynthia Petrossian"
date: "3/14/2022"
output: 
  html_document:
    toc: TRUE
    toc_float: TRUE
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, 
                      warning = FALSE, 
                      message = FALSE,
                      fig.path = "../Outputs/")
```

# Load Libraries
```{r}
library(tidyverse)
library(here)
library(tidytuesdayR)
library(ggbump)
library(ggdogs)
```

# Read In Data
```{r}
breed_rank_all <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2022/2022-02-01/breed_rank.csv')
view(breed_rank_all)
```

# Data Analysis
```{r}
pop <- breed_rank_all %>% #create top10
   pivot_longer(`2013 Rank`:`2020 Rank`, #pivot longer, selecting 2013:2020 columns
               names_to = "year", #put those into new column called year
               values_to = "rank") %>% #put rank values into new column called rank
  mutate(year = parse_number(year)) %>% #Remove word "Rank" from year column contents
  slice(1:80) #use only first 80 rows
```

# Making A Bad Plot
```{r badplot}
ggplot(pop, aes(x = year, #create ggplot using pop data, x is year
                y = rank, #y is rank
                group = Breed)) + #group is Breed
  geom_line(aes(color = Breed), size = 2) + #geom line, color by Breed, size 2
  geom_dog(aes(color = Breed), dog = "husky_2", size = 3)+ #geom dog, choose husky, size 4
  theme(plot.background = element_rect(fill = "red"), #make plot bg red
        panel.background = element_rect(fill = "green"), #make panel bg green
        legend.background = element_rect(fill = "green"), #make legend bg green
        plot.title = element_text(color = "hotpink1"),
        plot.subtitle = element_text(color = "hotpink1"),
        plot.caption = element_text(color = "hotpink1"),
        legend.title = element_text(color = "yellowgreen"),
        legend.text = element_text(color = "yellowgreen"),
        axis.text.y = element_text(color = "hotpink1"),
        axis.text.x = element_text(color = "hotpink1"),
        axis.title.y = element_text(color = "hotpink1"),
        axis.title.x = element_text(color = "hotpink1"))+ #change font
  labs(title = "popular dogs", #add title
       y = "how gud r they", #change y axis title
       x = "the continuous passage of time")+ #change x axis title
  scale_y_discrete()
```

This plot is a bad plot because  

* The points are too large and cover one another 
* The points are so large they also cover the line graph  
* The background colors are are not pleasant on the eye  
* The text colors are not easily readable  
* The axis titles are not clear

# Making A Good Plot
```{r goodplot}
ggplot()+ #create ggplot
  geom_bump(data = pop, #geom bump, using pop data
            mapping = aes(x = year, #x is year
                          y = rank, #y is rank
                          group = Breed, #group by Breed
                          color = Breed, #color by Breed
                          alpha = 1), #alpha is 1
            smooth = 15, size = 4.25)+ #smooth bump lines to 15 and size is 4.25
  scale_y_reverse(breaks = 1:13)+ #reverse y axis and add tick marks 1-13
  guides(alpha = FALSE)+ #remove alpha legend
  labs(title = "Most Popular Dog Breeds - Ranked", #add title
       subtitle = "2013 - 2020", #add subtitle
       y = "Rank", #change y axis title
       x = "Year", #xhange x axis title
       caption = "Source: American Kennel Club") #add source caption
```

This plot is a good plot because

* The background color is pleasing on the eye and everything is clearly visible
* The text color is clearly visible on the background
* The bump chart lines are clearly visible
* The different colors are easily distinguishable from one another
* The legend is clear
* The titles (main, sub, axes) are understandable and meaningful